---
title: "GenAI Policy Comparative Analysis"
subtitle: "NYC vs. Hong Kong — R Visualization"
---

# Install and load packages

```{r setup, message=FALSE, warning=FALSE}
packages <- c(
  "tidyverse",
  "janitor",
  "lubridate",
  "scales",
  "knitr",
  "patchwork"
)

to_install <- packages[!(packages %in% installed.packages()[, "Package"])]

if (length(to_install) > 0) {
  install.packages(to_install)
}

library(tidyverse)
library(janitor)
library(lubridate)
library(scales)
library(knitr)

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 9,
  fig.height = 5.5
)
```

# 1. Load `new.csv`

```{r load-csv}
# Main data source
path <- "GenAI_Policy_Comparative_LearningAnalytics_Reformatted.csv"

if (!file.exists(path)) {
  path <- "/mnt/data/GenAI_Policy_Comparative_LearningAnalytics_Reformatted.csv"
}

if (!file.exists(path)) {
  path <- file.choose()
}

policies_all <- read_csv(path, show_col_types = FALSE) %>%
  clean_names()
```

# 2. Helper functions

```{r helper-functions}
clean_text <- function(x) {
  x %>%
    as.character() %>%
    str_squish() %>%
    na_if("") %>%
    na_if("NA") %>%
    na_if("N/A") %>%
    na_if("NULL")
}

parse_publication_year <- function(x) {
  x <- clean_text(x)

  excel_numeric <- suppressWarnings(as.numeric(x))

  year_from_excel <- case_when(
    !is.na(excel_numeric) & excel_numeric > 30000 ~
      year(as.Date(excel_numeric, origin = "1899-12-30")),
    TRUE ~ NA_integer_
  )

  year_from_text <- case_when(
    is.na(year_from_excel) ~ str_extract(x, "(19|20)\\d{2}") %>% as.integer(),
    TRUE ~ NA_integer_
  )

  coalesce(year_from_excel, year_from_text)
}

parse_no_ai_flag <- function(x) {
  x <- clean_text(x)

  case_when(
    is.na(x) ~ FALSE,
    str_to_lower(x) %in% c("1", "yes", "true", "y") ~ TRUE,
    str_detect(str_to_lower(x), "no ai") ~ TRUE,
    TRUE ~ FALSE
  )
}

standardize_tier <- function(x) {
  x <- clean_text(x)
  x_lower <- str_to_lower(x)

  case_when(
    str_detect(x_lower, "national|federal") ~ "National/Federal",
    str_detect(x_lower, "city|territory|state|hksar|new york") ~ "City/Territory",
    str_detect(x_lower, "institution") ~ "Institutional",
    str_detect(x_lower, "faculty|school|department") ~ "Faculty/Department",
    str_detect(x_lower, "course") ~ "Course-wide",
    TRUE ~ x
  )
}

standardize_stance <- function(x) {
  x <- clean_text(x)
  x_lower <- str_to_lower(x)

  case_when(
    str_detect(x_lower, "prohibitive") ~ "Prohibitive",
    str_detect(x_lower, "cautious") ~ "Cautious",
    str_detect(x_lower, "functional") ~ "Functional",
    str_detect(x_lower, "encouraging") ~ "Encouraging",
    str_detect(x_lower, "not specified|unspecified") ~ "Not specified",
    TRUE ~ x
  )
}

make_safe_filename <- function(x) {
  x %>%
    str_to_lower() %>%
    str_replace_all("[^a-z0-9]+", "_") %>%
    str_replace_all("_$", "")
}
```

# 3. Clean data for visualization

```{r clean-data}
if (!"no_ai_teaching_content_is_not_ai_policy" %in% names(policies_all)) {
  policies_all$no_ai_teaching_content_is_not_ai_policy <- NA_character_
}

if (!"source_tab" %in% names(policies_all)) {
  policies_all$source_tab <- "new.csv"
}

policies <- policies_all %>%
  mutate(
    across(everything(), clean_text),

    no_ai_flag = parse_no_ai_flag(no_ai_teaching_content_is_not_ai_policy),

    region = case_when(
      str_to_lower(region) %in% c("nyc", "new york city") ~ "NYC",
      str_to_lower(region) %in% c("hong kong", "hk") ~ "Hong Kong",
      TRUE ~ region
    ),

    tier = standardize_tier(tier),
    stance = standardize_stance(stance),

    # Remove duplicate discretion label
    discretion = str_replace(
      clean_text(discretion),
      regex("faculty/dept decides", ignore_case = TRUE),
      "Faculty/Department decides"
    ),

    tier = factor(
      tier,
      levels = c(
        "National/Federal",
        "City/Territory",
        "Institutional",
        "Faculty/Department",
        "Course-wide"
      )
    ),

    stance = factor(
      stance,
      levels = c(
        "Prohibitive",
        "Cautious",
        "Functional",
        "Encouraging",
        "Not specified"
      )
    ),

    stance_score = case_when(
      !is.na(suppressWarnings(as.numeric(stance_number))) ~ suppressWarnings(as.numeric(stance_number)),
      stance == "Prohibitive" ~ 0,
      stance == "Cautious" ~ 1,
      stance == "Functional" ~ 2,
      stance == "Encouraging" ~ 3,
      TRUE ~ NA_real_
    ),

    publication_year = parse_publication_year(publication_date),

    institution_group = coalesce(
      clean_text(institution),
      clean_text(jurisdiction_institution),
      "Unspecified / government-wide"
    ),

    any_disclosure = disclosure %in% c(
      "Required",
      "Recommended",
      "Conditional"
    ),

    required_disclosure = disclosure == "Required",

    strong_enforcement = enforcement %in% c(
      "Explicit penalties",
      "Referenced to integrity code"
    ),

    learning_focus = focus_primary %in% c(
      "Pedagogy/Learning",
      "AI Literacy",
      "Professional Readiness"
    ),

    governance_focus = focus_primary %in% c(
      "Academic Integrity",
      "Privacy/Data/Ethics"
    )
  )

# Exclude rows marked as "No AI" or teaching content not considered policy
policies_clean <- policies %>%
  filter(no_ai_flag == FALSE)

# Core variables used in the visualizations
code_vars <- c(
  "tier",
  "stance",
  "disclosure",
  "discretion",
  "focus_primary",
  "focus_secondary",
  "enforcement",
  "coverage",
  "document_type"
)

code_vars <- code_vars[code_vars %in% names(policies_clean)]
```

# 4. Histogram-style count plots by region

```{r histogram-functions}
plot_count_histogram <- function(data, variable, title_text = NULL) {

  if (is.null(title_text)) {
    title_text <- paste("Histogram-style Counts:", str_to_title(str_replace_all(variable, "_", " ")))
  }

  data %>%
    filter(!is.na(region), !is.na(.data[[variable]])) %>%
    mutate(category = as.factor(.data[[variable]])) %>%
    ggplot(aes(x = category, fill = region)) +
    geom_bar(position = position_dodge(width = 0.8), width = 0.7) +
    geom_text(
      stat = "count",
      aes(label = after_stat(count)),
      position = position_dodge(width = 0.8),
      vjust = -0.3,
      size = 3
    ) +
    labs(
      title = title_text,
      x = str_to_title(str_replace_all(variable, "_", " ")),
      y = "Number of documents",
      fill = "Region"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(face = "bold", size = 14),
      axis.text.x = element_text(angle = 30, hjust = 1)
    )
}

plot_pct_bar <- function(data, variable, title_text, legend_title = NULL) {

  data %>%
    filter(!is.na(.data[[variable]])) %>%
    mutate(category = as.factor(.data[[variable]])) %>%
    count(region, category, name = "n") %>%
    group_by(region) %>%
    mutate(pct = n / sum(n)) %>%
    ungroup() %>%
    ggplot(aes(x = region, y = pct, fill = category)) +
    geom_col(width = 0.7, color = "white") +
    geom_text(
      aes(label = if_else(pct >= 0.06, percent(pct, accuracy = 1), "")),
      position = position_stack(vjust = 0.5),
      size = 3.4
    ) +
    scale_y_continuous(labels = percent_format()) +
    labs(
      title = title_text,
      x = NULL,
      y = "Percent of documents",
      fill = ifelse(
        is.null(legend_title),
        str_to_title(str_replace_all(variable, "_", " ")),
        legend_title
      )
    ) +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(face = "bold", size = 14),
      legend.text = element_text(size = 9)
    )
}
```

```{r histograms-main}
histogram_plots <- map(
  code_vars,
  ~ plot_count_histogram(
    policies_clean,
    .x,
    paste("Histogram-style Counts of", str_to_title(str_replace_all(.x, "_", " ")), "by Region")
  )
)

names(histogram_plots) <- code_vars

histogram_plots$stance
histogram_plots$disclosure
histogram_plots$enforcement
histogram_plots$focus_primary
histogram_plots$tier
```

# 5. Percentage comparisons: NYC vs. Hong Kong

```{r percentage-plots}
fig_1_stance <- plot_pct_bar(
  policies_clean %>% filter(stance != "Not specified"),
  "stance",
  "Policy Stance by Region",
  "Policy stance"
)

fig_2_disclosure <- plot_pct_bar(
  policies_clean,
  "disclosure",
  "Disclosure Expectations by Region",
  "Disclosure expectation"
)

fig_3_enforcement <- plot_pct_bar(
  policies_clean,
  "enforcement",
  "Enforcement Approach by Region",
  "Enforcement approach"
)

fig_4_focus <- plot_pct_bar(
  policies_clean,
  "focus_primary",
  "Primary Policy Focus by Region",
  "Primary focus"
)

fig_1_stance
fig_2_disclosure
fig_3_enforcement
fig_4_focus
```

# 6. Governance tier by stance

```{r stance-by-tier}
stance_by_tier <- policies_clean %>%
  filter(!is.na(region), !is.na(tier), !is.na(stance)) %>%
  count(region, tier, stance, name = "n") %>%
  group_by(region, tier) %>%
  mutate(
    pct = n / sum(n),
    pct_label = percent(pct, accuracy = 1)
  ) %>%
  ungroup()

fig_6_stance_by_tier <- ggplot(
  stance_by_tier,
  aes(x = tier, y = pct, fill = stance)
) +
  geom_col(color = "white") +
  geom_text(
    aes(label = if_else(pct >= 0.06, pct_label, "")),
    position = position_stack(vjust = 0.5),
    size = 3
  ) +
  facet_wrap(~ region) +
  coord_flip() +
  scale_y_continuous(labels = percent_format()) +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  labs(
    title = "Policy Stance by Governance Tier and Region",
    x = NULL,
    y = "Percent of documents within tier",
    fill = "Policy stance"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", size = 14),
    strip.text = element_text(face = "bold", size = 12)
  )

fig_6_stance_by_tier
```

```{r stance-by-tier-stacked-100}
# 100% stacked bar: stance by tier, faceted by region
stance_colors <- c(
  "Prohibitive" = "#C0392B",
  "Cautious"    = "#E67E22",
  "Functional"  = "#95A5A6",
  "Encouraging" = "#27AE60"
)

plot_data_100 <- policies_clean %>%
  filter(
    !is.na(region),
    !is.na(tier),
    !is.na(stance),
    stance != "Not specified"
  ) %>%
  mutate(
    stance = factor(stance, levels = names(stance_colors)),
    region = factor(region, levels = c("Hong Kong", "NYC"))
  )

stance_by_tier_100 <- plot_data_100 %>%
  count(region, tier, stance, .drop = FALSE) %>%
  group_by(region, tier) %>%
  mutate(
    pct = if (sum(n) > 0) n / sum(n) else rep(NA_real_, dplyr::n()),
    pct_label = if_else(!is.na(pct) & pct >= 0.06, percent(pct, accuracy = 1), "")
  ) %>%
  ungroup()

fig_6b_stacked_100 <- ggplot(
  stance_by_tier_100,
  aes(x = tier, y = pct, fill = stance)
) +
  geom_col(width = 0.7, colour = "white", linewidth = 0.5) +
  geom_text(
    aes(label = pct_label),
    position = position_stack(vjust = 0.5),
    colour   = "white",
    fontface = "bold",
    size     = 3.2
  ) +
  facet_wrap(~ region, ncol = 2) +
  coord_flip() +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1.02),
    expand = c(0, 0)
  ) +
  scale_fill_manual(
    values = stance_colors,
    breaks = names(stance_colors),
    name   = "Policy Stance"
  ) +
  labs(
    title    = "Policy Stance by Governance Tier — 100% Stacked",
    subtitle = "Hong Kong vs. New York City",
    x        = NULL,
    y        = "Percentage of documents within tier"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14),
    plot.subtitle      = element_text(size = 11, colour = "grey40"),
    strip.text         = element_text(face = "bold", size = 12),
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold"),
    panel.grid.major.y = element_blank()
  ) +
  guides(fill = guide_legend(nrow = 1))

fig_6b_stacked_100
```

# 7. Heatmap of Policy Stance by Governance Tier

```{r stance-tier-heatmap}
fig_7_heatmap <- stance_by_tier %>%
  ggplot(aes(x = stance, y = tier, fill = pct)) +
  geom_tile(color = "white") +
  geom_text(aes(label = percent(pct, accuracy = 1)), size = 3.3) +
  facet_wrap(~ region) +
  scale_fill_continuous(labels = percent_format()) +
  labs(
    title = "Heatmap of Policy Stance by Governance Tier",
    x = "Policy stance",
    y = "Governance tier",
    fill = "Percent"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 30, hjust = 1),
    strip.text = element_text(face = "bold", size = 12)
  )

fig_7_heatmap
```

# 8. Within-city comparisons by institution / jurisdiction

```{r within-city-functions}
plot_within_city <- function(data, region_value, variable) {

  data %>%
    filter(
      region == region_value,
      !is.na(institution_group),
      !is.na(.data[[variable]])
    ) %>%
    mutate(category = .data[[variable]]) %>%
    count(institution_group, category, name = "n") %>%
    group_by(institution_group) %>%
    mutate(
      pct = n / sum(n),
      pct_label = percent(pct, accuracy = 1)
    ) %>%
    ungroup() %>%
    ggplot(aes(x = reorder(institution_group, pct), y = pct, fill = category)) +
    geom_col(width = 0.7, color = "white") +
    geom_text(
      aes(label = if_else(pct >= 0.08, pct_label, "")),
      position = position_stack(vjust = 0.5),
      size = 2.8
    ) +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    labs(
      title = paste(
        region_value,
        str_to_title(str_replace_all(variable, "_", " ")),
        "by Institution / Jurisdiction"
      ),
      x = NULL,
      y = "Percent of documents within institution/jurisdiction",
      fill = str_to_title(str_replace_all(variable, "_", " "))
    ) +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      legend.text = element_text(size = 8),
      plot.title = element_text(face = "bold", size = 13)
    )
}
```

```{r within-city-plots}
nyc_disclosure_institution <- plot_within_city(policies_clean, "NYC", "disclosure")
hk_disclosure_institution <- plot_within_city(policies_clean, "Hong Kong", "disclosure")

nyc_stance_institution <- plot_within_city(policies_clean, "NYC", "stance")
hk_stance_institution <- plot_within_city(policies_clean, "Hong Kong", "stance")

nyc_disclosure_institution
hk_disclosure_institution
nyc_stance_institution
hk_stance_institution
```

# 9. Binary policy feature comparison visualization

```{r binary-feature-visualization}
binary_vars <- c(
  "any_disclosure",
  "required_disclosure",
  "strong_enforcement",
  "learning_focus",
  "governance_focus"
)

binary_summary <- policies_clean %>%
  select(region, all_of(binary_vars)) %>%
  pivot_longer(
    cols = all_of(binary_vars),
    names_to = "policy_feature",
    values_to = "value"
  ) %>%
  group_by(policy_feature, region) %>%
  summarise(
    n_yes = sum(value, na.rm = TRUE),
    total = n(),
    pct_yes = n_yes / total,
    .groups = "drop"
  ) %>%
  mutate(
    pct_label = percent(pct_yes, accuracy = 0.1),
    policy_feature = recode(
      policy_feature,
      any_disclosure = "Any disclosure expected",
      required_disclosure = "Disclosure required",
      strong_enforcement = "Strong enforcement",
      learning_focus = "Learning-oriented focus",
      governance_focus = "Governance/integrity focus"
    )
  )

fig_8_binary <- ggplot(
  binary_summary,
  aes(x = policy_feature, y = pct_yes, fill = region)
) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_text(
    aes(label = percent(pct_yes, accuracy = 1)),
    position = position_dodge(width = 0.8),
    vjust = -0.3,
    size = 3.5
  ) +
  coord_flip() +
  scale_y_continuous(labels = percent_format(), limits = c(0, 1)) +
  labs(
    title = "Key Policy Features by Region",
    x = NULL,
    y = "Percent of documents",
    fill = "Region"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", size = 14)
  )

fig_8_binary
```

# 10. 100% stacked bar by institution, separate plots for HK and NYC
```{r}

# Clean institution names and combine Columbia + Columbia University and remove other institutions
plot_data_clean <- plot_data_100 %>%
  mutate(
    institution = str_squish(institution),
    institution = case_when(
      str_to_lower(institution) %in% c("columbia", "columbia university") ~ "Columbia University",
      TRUE ~ institution
    ),
    stance = str_squish(stance),
    stance = factor(
      stance,
      levels = c("Encouraging", "Functional", "Cautious", "Prohibitive")
    )
  ) %>%
  filter(
  !is.na(region),
  !is.na(institution),
  institution != "",
  !institution %in% c("NYCPS", "OTI"),
  !is.na(stance)
)

# Calculate percentages
institution_stance <- plot_data_clean %>%
  count(region, institution, stance, name = "n") %>%
  group_by(region, institution) %>%
  complete(
    stance = factor(
      c("Encouraging", "Functional", "Cautious", "Prohibitive"),
      levels = c("Encouraging", "Functional", "Cautious", "Prohibitive")
    ),
    fill = list(n = 0)
  ) %>%
  mutate(
    pct = n / sum(n),
    pct_label = if_else(n > 0 & pct >= 0.06, percent(pct, accuracy = 1), "")
  ) %>%
  ungroup()

# Colors
stance_colors <- c(
  "Encouraging" = "#259E45",
  "Functional" = "#93A3A2",
  "Cautious" = "#E16A12",
  "Prohibitive" = "#B22222"
)

# Function to make graph
make_institution_plot <- function(data, selected_region, title_text) {
  data %>%
    filter(region == selected_region) %>%
    ggplot(aes(x = institution, y = pct, fill = stance)) +
    geom_col(width = 0.6, color = "white") +
    geom_text(
      aes(label = pct_label),
      position = position_stack(vjust = 0.5),
      color = "white",
      fontface = "bold",
      size = 3.5
    ) +
    scale_y_continuous(
      labels = percent_format(accuracy = 1),
      limits = c(0, 1),
      expand = expansion(mult = c(0, 0.02))
    ) +
    scale_fill_manual(
      values = stance_colors,
      drop = FALSE,
      name = "Policy Stance"
    ) +
    labs(
      title = title_text,
      x = "Institution",
      y = "Percentage of documents"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 9),
      axis.text.x = element_text(angle = 20, hjust = 1),
      legend.title = element_text(face = "bold"),
      panel.grid.major.x = element_blank()
    )
}

# Hong Kong first
hk_stance_institution <- make_institution_plot(
  institution_stance,
  "Hong Kong",
  "Hong Kong — Policy Stance by Institution"
)

# NYC second
nyc_stance_institution <- make_institution_plot(
  institution_stance,
  "NYC",
  "NYC — Policy Stance by Institution"
)

# Side-by-side plot
patchwork::wrap_plots(
  hk_stance_institution,
  nyc_stance_institution,
  ncol = 2,
  guides = "collect"
) &
  theme(legend.position = "right")
```


# 11. Coverage and discretion graphs

```{r coverage-discretion}
fig_10_coverage <- plot_pct_bar(
  policies_clean,
  "coverage",
  "Figure 10. Coverage of GenAI Policy Documents by Region",
  "Coverage"
)

fig_11_discretion <- plot_pct_bar(
  policies_clean,
  "discretion",
  "Policy Discretion by Region",
  "Discretion"
)

fig_10_coverage
fig_11_discretion
```

