---
title: "GenAI Policy Comparative Analysis"
subtitle: "NYC vs. Hong Kong — Statistical Analysis in Rstudio"
---

# 1. Setup

```{r setup, message=FALSE, warning=FALSE}
packages <- c(
  "tidyverse",
  "janitor",
  "broom",
  "car",
  "knitr",
  "writexl",
  "readr"
)

to_install <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(to_install) > 0) {
  install.packages(to_install)
}

library(tidyverse)
library(janitor)
library(broom)
library(car)
library(knitr)
library(writexl)
library(readr)

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# 2. Load data

```{r load-data}
path <- "GenAI_Policy_Comparative_LearningAnalytics_Reformatted.csv"

if (!file.exists(path)) {
  path <- "/mnt/data/GenAI_Policy_Comparative_LearningAnalytics_Reformatted.csv"
}

if (!file.exists(path)) {
  path <- file.choose()
}

raw_df <- read_csv(path, show_col_types = FALSE)

glimpse(raw_df)
```

# 3. Helper functions

```{r helper-functions}
clean_text <- function(x) {
  x %>%
    as.character() %>%
    str_replace_all("\\r\\n|\\n|\\r", " ") %>%
    str_squish() %>%
    na_if("") %>%
    na_if("NA") %>%
    na_if("N/A") %>%
    na_if("NULL")
}

fmt_p <- function(p) {
  case_when(
    is.na(p) ~ NA_character_,
    p < .001 ~ "< .001",
    TRUE ~ paste0("= ", sprintf("%.3f", p))
  )
}

cramers_v_from_table <- function(tab) {
  if (nrow(tab) < 2 || ncol(tab) < 2 || sum(tab) == 0) {
    return(NA_real_)
  }

  chi <- suppressWarnings(chisq.test(tab, correct = FALSE))
  chi_sq <- as.numeric(chi$statistic)
  n <- sum(tab)
  min_dim <- min(nrow(tab), ncol(tab)) - 1

  if (min_dim <= 0) {
    return(NA_real_)
  }

  sqrt(chi_sq / (n * min_dim))
}

safe_type2_anova <- function(model) {
  out <- tryCatch(
    broom::tidy(car::Anova(model, type = 2)),
    error = function(e) {
      message("Type II ANOVA failed; returning base R anova() table instead. Error: ", e$message)
      broom::tidy(anova(model))
    }
  )

  out
}

standardize_institution <- function(x) {
  case_when(
    is.na(x) ~ NA_character_,
    x %in% c("Columbia", "Columbia University") ~ "Columbia University",
    x == "NYU" ~ "NYU",
    x == "CUNY" ~ "CUNY",
    str_detect(str_to_lower(x), "hku|hong kong univ") ~ "HKU",
    str_detect(str_to_lower(x), "polyu|polytechnic") ~ "PolyU",
    str_detect(str_to_lower(x), "lingnan") ~ "Lingnan",
    TRUE ~ x
  )
}
```

# 4. Clean and prepare data

```{r clean-data}
policy_df <- raw_df %>%
  clean_names() %>%
  mutate(
    across(everything(), clean_text),

    region = case_when(
      str_to_lower(region) %in% c("nyc", "new york city") ~ "NYC",
      str_to_lower(region) %in% c("hong kong", "hk") ~ "Hong Kong",
      TRUE ~ region
    ),

    tier = case_when(
      str_detect(str_to_lower(tier), "national|federal") ~ "National/Federal",
      str_detect(str_to_lower(tier), "city|territory|state|hksar|new york") ~ "City/Territory",
      str_detect(str_to_lower(tier), "institution") ~ "Institutional",
      str_detect(str_to_lower(tier), "faculty|school|department") ~ "Faculty/Department",
      str_detect(str_to_lower(tier), "course") ~ "Course-wide",
      TRUE ~ tier
    ),

    stance = case_when(
      str_detect(str_to_lower(stance), "prohibitive") ~ "Prohibitive",
      str_detect(str_to_lower(stance), "cautious") ~ "Cautious",
      str_detect(str_to_lower(stance), "functional") ~ "Functional",
      str_detect(str_to_lower(stance), "encouraging") ~ "Encouraging",
      str_detect(str_to_lower(stance), "not specified|unspecified") ~ "Not specified",
      TRUE ~ stance
    ),

    discretion = str_replace(
      discretion,
      regex("faculty/dept decides", ignore_case = TRUE),
      "Faculty/Department decides"
    ),

    institution_group = coalesce(institution, jurisdiction_institution),
    institution_group = standardize_institution(institution_group),

    tier_numeric = suppressWarnings(as.numeric(tier_number)),
    stance_numeric = suppressWarnings(as.numeric(stance_number)),

    tier_numeric = if_else(
      is.na(tier_numeric),
      case_when(
        tier == "National/Federal" ~ 1,
        tier == "City/Territory" ~ 2,
        tier == "Institutional" ~ 3,
        tier == "Faculty/Department" ~ 4,
        tier == "Course-wide" ~ 5,
        TRUE ~ NA_real_
      ),
      tier_numeric
    ),

    stance_numeric = if_else(
      is.na(stance_numeric),
      case_when(
        stance == "Prohibitive" ~ 0,
        stance == "Cautious" ~ 1,
        stance == "Functional" ~ 2,
        stance == "Encouraging" ~ 3,
        TRUE ~ NA_real_
      ),
      stance_numeric
    ),

    tier_factor = factor(
      tier,
      levels = c(
        "National/Federal",
        "City/Territory",
        "Institutional",
        "Faculty/Department",
        "Course-wide"
      )
    ),

    stance_factor = factor(
      stance,
      levels = c(
        "Prohibitive",
        "Cautious",
        "Functional",
        "Encouraging"
      )
    ),

    region = factor(region, levels = c("NYC", "Hong Kong")),
    governance_domain = factor(governance_domain)
  )

# Exclude "Not specified" rows
analysis_df <- policy_df %>%
  filter(stance != "Not specified")

sample_size <- analysis_df %>%
  count(region, name = "n_documents")

sample_size %>% kable()
```

# 5. Data quality checks

```{r data-quality}
missing_summary <- analysis_df %>%
  summarise(
    total_documents = n(),
    missing_id = sum(is.na(id)),
    missing_region = sum(is.na(region)),
    missing_tier = sum(is.na(tier)),
    missing_tier_numeric = sum(is.na(tier_numeric)),
    missing_stance = sum(is.na(stance)),
    missing_stance_numeric = sum(is.na(stance_numeric)),
    missing_institution = sum(is.na(institution)),
    missing_institution_group = sum(is.na(institution_group)),
    missing_document_type = sum(is.na(document_type)),
    missing_disclosure = sum(is.na(disclosure)),
    missing_discretion = sum(is.na(discretion)),
    missing_focus_primary = sum(is.na(focus_primary)),
    missing_focus_secondary = sum(is.na(focus_secondary)),
    missing_enforcement = sum(is.na(enforcement)),
    missing_coverage = sum(is.na(coverage)),
    missing_source_url = sum(is.na(source_url))
  )

missing_summary %>% kable()

duplicate_ids <- analysis_df %>%
  count(id, name = "n") %>%
  filter(n > 1, !is.na(id))

duplicate_urls <- analysis_df %>%
  count(source_url, name = "n") %>%
  filter(n > 1, !is.na(source_url))

duplicate_ids %>% kable()
duplicate_urls %>% kable()
```

# 6. Descriptive summaries

```{r descriptive-summaries}
region_counts <- analysis_df %>%
  count(region, name = "count")

region_counts %>% kable()

stance_counts_by_region <- analysis_df %>%
  count(region, stance, name = "n") %>%
  group_by(region) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup()

stance_counts_by_region %>% kable(digits = 3)

tier_counts_by_region <- analysis_df %>%
  count(region, tier_factor, name = "n") %>%
  group_by(region) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup()

tier_counts_by_region %>% kable(digits = 3)

stance_descriptives <- analysis_df %>%
  filter(!is.na(stance_numeric)) %>%
  group_by(region) %>%
  summarise(
    n = n(),
    mean = mean(stance_numeric),
    median = median(stance_numeric),
    sd = sd(stance_numeric),
    min = min(stance_numeric),
    max = max(stance_numeric),
    pct_prohibitive = mean(stance_numeric == 0),
    pct_encouraging = mean(stance_numeric == 3),
    .groups = "drop"
  )

stance_descriptives %>% kable(digits = 3)

stance_by_tier_descriptives <- analysis_df %>%
  filter(!is.na(stance_numeric), !is.na(tier_factor)) %>%
  group_by(region, tier_factor) %>%
  summarise(
    n = n(),
    mean = mean(stance_numeric),
    median = median(stance_numeric),
    sd = sd(stance_numeric),
    .groups = "drop"
  )

stance_by_tier_descriptives %>% kable(digits = 3)
```

# 7. Two-way ANOVA: stance by tier and region

This section replicates the notebook's Type II ANOVA for `Stance_Numeric ~ C(Tier_Numeric) + C(Region) + C(Tier_Numeric):C(Region)`.

```{r anova-tier-region}
anova_df_full <- analysis_df %>%
  filter(!is.na(stance_numeric), !is.na(tier_factor), !is.na(region)) %>%
  mutate(
    tier_factor = factor(tier_factor),
    region = factor(region)
  )

anova_tier_region_model <- lm(stance_numeric ~ tier_factor * region, data = anova_df_full)

anova_tier_region <- safe_type2_anova(anova_tier_region_model) %>%
  mutate(p_apa = fmt_p(p.value))

anova_tier_region %>% kable(digits = 3)
```

# 8. Overall Mann-Whitney U test: stance by region

```{r mann-whitney-overall}
mann_whitney_overall <- wilcox.test(
  stance_numeric ~ region,
  data = anova_df_full,
  exact = FALSE
)

mann_whitney_overall_table <- tibble(
  comparison = "NYC vs Hong Kong",
  statistic_w = unname(mann_whitney_overall$statistic),
  p_value = mann_whitney_overall$p.value,
  p_apa = fmt_p(mann_whitney_overall$p.value),
  nyc_median = median(anova_df_full$stance_numeric[anova_df_full$region == "NYC"], na.rm = TRUE),
  hong_kong_median = median(anova_df_full$stance_numeric[anova_df_full$region == "Hong Kong"], na.rm = TRUE),
  nyc_mean = mean(anova_df_full$stance_numeric[anova_df_full$region == "NYC"], na.rm = TRUE),
  hong_kong_mean = mean(anova_df_full$stance_numeric[anova_df_full$region == "Hong Kong"], na.rm = TRUE)
)

mann_whitney_overall_table %>% kable(digits = 3)
```

# 9. Kendall's Tau: tier and stance

```{r kendall-tau}
kendall_df <- anova_df_full %>%
  filter(!is.na(tier_numeric), !is.na(stance_numeric))

kendall_result <- cor.test(
  kendall_df$tier_numeric,
  kendall_df$stance_numeric,
  method = "kendall",
  exact = FALSE
)

kendall_table <- tibble(
  method = "Kendall's Tau",
  tau = unname(kendall_result$estimate),
  p_value = kendall_result$p.value,
  p_apa = fmt_p(kendall_result$p.value),
  n = nrow(kendall_df)
)

kendall_table %>% kable(digits = 3)
```

# 10. Institution-by-tier ANOVA tables

```{r institution-tier-anova}
anova_df_institutions <- analysis_df %>%
  filter(!is.na(stance_numeric), !is.na(tier_factor), !is.na(institution_group)) %>%
  mutate(
    institution_group = factor(institution_group),
    tier_factor = factor(tier_factor)
  )

institution_tier_interaction_model <- lm(
  stance_numeric ~ institution_group * tier_factor,
  data = anova_df_institutions
)

institution_tier_interaction_anova <- safe_type2_anova(institution_tier_interaction_model) %>%
  mutate(p_apa = fmt_p(p.value))

institution_tier_interaction_anova %>% kable(digits = 3)

institution_tier_main_effects_model <- lm(
  stance_numeric ~ institution_group + tier_factor,
  data = anova_df_institutions
)

institution_tier_main_effects_anova <- safe_type2_anova(institution_tier_main_effects_model) %>%
  mutate(p_apa = fmt_p(p.value))

institution_tier_main_effects_anova %>% kable(digits = 3)
```

# 11. One-way ANOVA: institutional differences within each tier

```{r one-way-anova-by-tier}
run_oneway_anova_by_tier <- function(data, tier_value) {
  tier_subset <- data %>%
    filter(tier_factor == tier_value) %>%
    droplevels()

  n_institutions <- n_distinct(tier_subset$institution_group)

  if (nrow(tier_subset) <= n_institutions || n_institutions < 2) {
    return(tibble(
      tier = as.character(tier_value),
      n = nrow(tier_subset),
      n_institutions = n_institutions,
      term = NA_character_,
      statistic = NA_real_,
      p_value = NA_real_,
      p_apa = NA_character_,
      note = "Skipped: not enough data for one-way ANOVA"
    ))
  }

  model <- lm(stance_numeric ~ institution_group, data = tier_subset)

  broom::tidy(anova(model)) %>%
    filter(term == "institution_group") %>%
    transmute(
      tier = as.character(tier_value),
      n = nrow(tier_subset),
      n_institutions = n_institutions,
      term = term,
      statistic = statistic,
      p_value = p.value,
      p_apa = fmt_p(p.value),
      note = NA_character_
    )
}

oneway_anova_by_tier <- map_dfr(
  levels(anova_df_institutions$tier_factor),
  ~ run_oneway_anova_by_tier(anova_df_institutions, .x)
)

oneway_anova_by_tier %>% kable(digits = 3)
```

# 12. Kruskal-Wallis tests: institutional differences within each tier

```{r kruskal-by-tier}
run_kruskal_by_tier <- function(data, tier_value, region_value = NULL) {
  test_data <- data %>%
    filter(tier_factor == tier_value)

  if (!is.null(region_value)) {
    test_data <- test_data %>% filter(region == region_value)
  }

  test_data <- test_data %>%
    filter(!is.na(stance_numeric), !is.na(institution_group)) %>%
    droplevels()

  n_institutions <- n_distinct(test_data$institution_group)

  if (nrow(test_data) < 2 || n_institutions < 2) {
    return(tibble(
      region = if (is.null(region_value)) "All regions" else as.character(region_value),
      tier = as.character(tier_value),
      n = nrow(test_data),
      n_institutions = n_institutions,
      statistic_h = NA_real_,
      p_value = NA_real_,
      p_apa = NA_character_,
      note = "Skipped: not enough data for Kruskal-Wallis"
    ))
  }

  result <- tryCatch(
    kruskal.test(stance_numeric ~ institution_group, data = test_data),
    error = function(e) NULL
  )

  if (is.null(result)) {
    return(tibble(
      region = if (is.null(region_value)) "All regions" else as.character(region_value),
      tier = as.character(tier_value),
      n = nrow(test_data),
      n_institutions = n_institutions,
      statistic_h = NA_real_,
      p_value = NA_real_,
      p_apa = NA_character_,
      note = "Skipped: test failed"
    ))
  }

  tibble(
    region = if (is.null(region_value)) "All regions" else as.character(region_value),
    tier = as.character(tier_value),
    n = nrow(test_data),
    n_institutions = n_institutions,
    statistic_h = unname(result$statistic),
    p_value = result$p.value,
    p_apa = fmt_p(result$p.value),
    note = NA_character_
  )
}

kruskal_all_regions_by_tier <- map_dfr(
  levels(anova_df_institutions$tier_factor),
  ~ run_kruskal_by_tier(anova_df_institutions, .x)
)

kruskal_by_region_tier <- crossing(
  region = levels(droplevels(anova_df_institutions$region)),
  tier = levels(anova_df_institutions$tier_factor)
) %>%
  pmap_dfr(\(region, tier) run_kruskal_by_tier(anova_df_institutions, tier, region))

kruskal_all_regions_by_tier %>% kable(digits = 3)
kruskal_by_region_tier %>% kable(digits = 3)
```

# 13. Chi-square tests: nominal variables by region

```{r chi-square-nominal-by-region}
nominal_columns <- c(
  "document_type",
  "disclosure",
  "discretion",
  "focus_primary",
  "enforcement",
  "coverage"
)

run_chi_square <- function(data, variable) {
  test_data <- data %>%
    filter(!is.na(region), !is.na(.data[[variable]]))

  tab <- table(test_data$region, test_data[[variable]])

  if (nrow(tab) < 2 || ncol(tab) < 2) {
    return(tibble(
      variable = variable,
      n = sum(tab),
      chi_square = NA_real_,
      df = NA_real_,
      p_value = NA_real_,
      p_apa = NA_character_,
      cramers_v = NA_real_,
      note = "Skipped: insufficient table dimensions"
    ))
  }

  result <- suppressWarnings(chisq.test(tab, correct = FALSE))

  tibble(
    variable = variable,
    n = sum(tab),
    chi_square = unname(result$statistic),
    df = unname(result$parameter),
    p_value = result$p.value,
    p_apa = fmt_p(result$p.value),
    cramers_v = cramers_v_from_table(tab),
    note = NA_character_
  )
}

chi_square_nominal_by_region <- map_dfr(
  nominal_columns,
  ~ run_chi_square(anova_df_full, .x)
)

chi_square_nominal_by_region %>% kable(digits = 3)
```

# 14. Fisher / Monte Carlo exact tests: nominal variables by region

```{r fisher-nominal-by-region}
run_fisher_region <- function(data, variable) {
  test_data <- data %>%
    filter(!is.na(region), !is.na(.data[[variable]]))

  tab <- table(test_data$region, test_data[[variable]])

  if (nrow(tab) < 2 || ncol(tab) < 2) {
    return(tibble(
      variable = variable,
      n = sum(tab),
      fisher_p = NA_real_,
      fisher_p_apa = NA_character_,
      cramers_v = NA_real_,
      note = "Skipped: insufficient table dimensions"
    ))
  }

  fisher_result <- fisher.test(tab, simulate.p.value = TRUE, B = 10000)

  tibble(
    variable = variable,
    n = sum(tab),
    fisher_p = fisher_result$p.value,
    fisher_p_apa = fmt_p(fisher_result$p.value),
    cramers_v = cramers_v_from_table(tab),
    note = NA_character_
  )
}

fisher_nominal_by_region <- map_dfr(
  nominal_columns,
  ~ run_fisher_region(anova_df_full, .x)
)

fisher_nominal_by_region %>% kable(digits = 3)
```

# 15. Fisher / Monte Carlo exact tests: selected nominal variables by tier and region

```{r fisher-by-tier}
nominal_columns_by_tier <- c(
  "focus_primary",
  "discretion",
  "document_type"
)

run_fisher_by_tier <- function(data, tier_value, variable) {
  test_data <- data %>%
    filter(tier_factor == tier_value, !is.na(region), !is.na(.data[[variable]])) %>%
    droplevels()

  tab <- table(test_data$region, test_data[[variable]])

  if (nrow(tab) < 2 || ncol(tab) < 2 || sum(tab) < 2) {
    return(tibble(
      tier = as.character(tier_value),
      variable = variable,
      n = sum(tab),
      fisher_p = NA_real_,
      fisher_p_apa = NA_character_,
      cramers_v = NA_real_,
      note = "Skipped: insufficient table dimensions"
    ))
  }

  fisher_result <- fisher.test(tab, simulate.p.value = TRUE, B = 10000)

  tibble(
    tier = as.character(tier_value),
    variable = variable,
    n = sum(tab),
    fisher_p = fisher_result$p.value,
    fisher_p_apa = fmt_p(fisher_result$p.value),
    cramers_v = cramers_v_from_table(tab),
    note = NA_character_
  )
}

fisher_nominal_by_tier <- crossing(
  tier = levels(anova_df_full$tier_factor),
  variable = nominal_columns_by_tier
) %>%
  pmap_dfr(\(tier, variable) run_fisher_by_tier(anova_df_full, tier, variable))

fisher_nominal_by_tier %>% kable(digits = 3)
```

# 16. Mann-Whitney U tests: stance by region within each tier

```{r mann-whitney-by-tier}
run_mann_whitney_by_tier <- function(data, tier_value) {
  test_data <- data %>%
    filter(tier_factor == tier_value, !is.na(stance_numeric), !is.na(region)) %>%
    droplevels()

  region_counts <- test_data %>%
    count(region, name = "n")

  if (n_distinct(test_data$region) < 2 || any(region_counts$n == 0)) {
    return(tibble(
      tier = as.character(tier_value),
      n = nrow(test_data),
      statistic_w = NA_real_,
      p_value = NA_real_,
      p_apa = NA_character_,
      nyc_median = NA_real_,
      hong_kong_median = NA_real_,
      nyc_mean = NA_real_,
      hong_kong_mean = NA_real_,
      note = "Skipped: both regions are required"
    ))
  }

  result <- wilcox.test(stance_numeric ~ region, data = test_data, exact = FALSE)

  tibble(
    tier = as.character(tier_value),
    n = nrow(test_data),
    statistic_w = unname(result$statistic),
    p_value = result$p.value,
    p_apa = fmt_p(result$p.value),
    nyc_median = median(test_data$stance_numeric[test_data$region == "NYC"], na.rm = TRUE),
    hong_kong_median = median(test_data$stance_numeric[test_data$region == "Hong Kong"], na.rm = TRUE),
    nyc_mean = mean(test_data$stance_numeric[test_data$region == "NYC"], na.rm = TRUE),
    hong_kong_mean = mean(test_data$stance_numeric[test_data$region == "Hong Kong"], na.rm = TRUE),
    note = NA_character_
  )
}

mann_whitney_by_tier <- map_dfr(
  levels(anova_df_full$tier_factor),
  ~ run_mann_whitney_by_tier(anova_df_full, .x)
)

mann_whitney_by_tier %>% kable(digits = 3)
```

# 17. Binary policy feature comparisons

```{r binary-policy-features}
binary_df <- analysis_df %>%
  mutate(
    any_disclosure = disclosure %in% c("Required", "Recommended", "Conditional"),
    required_disclosure = disclosure == "Required",
    strong_enforcement = enforcement %in% c("Explicit penalties", "Referenced to integrity code"),
    learning_focus = focus_primary %in% c("Pedagogy/Learning", "AI Literacy", "Professional Readiness"),
    governance_focus = focus_primary %in% c("Academic Integrity", "Privacy/Data/Ethics")
  )

binary_vars <- c(
  "any_disclosure",
  "required_disclosure",
  "strong_enforcement",
  "learning_focus",
  "governance_focus"
)

binary_summary <- binary_df %>%
  select(region, all_of(binary_vars)) %>%
  pivot_longer(
    cols = all_of(binary_vars),
    names_to = "policy_feature",
    values_to = "value"
  ) %>%
  group_by(policy_feature, region) %>%
  summarise(
    n_yes = sum(value, na.rm = TRUE),
    total = n(),
    pct_yes = n_yes / total,
    .groups = "drop"
  ) %>%
  mutate(
    policy_feature = dplyr::recode(
      policy_feature,
      any_disclosure = "Any disclosure expected",
      required_disclosure = "Disclosure required",
      strong_enforcement = "Strong enforcement",
      learning_focus = "Learning-oriented focus",
      governance_focus = "Governance/integrity focus"
    )
  )

binary_summary %>% kable(digits = 3)

run_binary_fisher <- function(data, variable) {
  test_data <- data %>%
    filter(!is.na(region), !is.na(.data[[variable]]))

  tab <- table(test_data$region, test_data[[variable]])

  if (nrow(tab) < 2 || ncol(tab) < 2) {
    return(tibble(
      indicator = variable,
      fisher_p = NA_real_,
      fisher_p_apa = NA_character_,
      note = "Skipped: insufficient table dimensions"
    ))
  }

  fisher_result <- fisher.test(tab)

  tibble(
    indicator = variable,
    fisher_p = fisher_result$p.value,
    fisher_p_apa = fmt_p(fisher_result$p.value),
    note = NA_character_
  )
}

binary_tests <- map_dfr(
  binary_vars,
  ~ run_binary_fisher(binary_df, .x)
)

binary_tests %>% kable(digits = 3)
```

# 18. Export all analysis tables - Reproducibility

```{r export-tables}
dir.create("genai_policy_outputs_newcsv", showWarnings = FALSE)

analysis_tables <- list(
  sample_size = sample_size,
  missing_summary = missing_summary,
  duplicate_ids = duplicate_ids,
  duplicate_urls = duplicate_urls,
  region_counts = region_counts,
  stance_counts_by_region = stance_counts_by_region,
  tier_counts_by_region = tier_counts_by_region,
  stance_descriptives = stance_descriptives,
  stance_by_tier_descriptives = stance_by_tier_descriptives,
  anova_tier_region = anova_tier_region,
  mann_whitney_overall = mann_whitney_overall_table,
  kendall_tau = kendall_table,
  institution_tier_interaction_anova = institution_tier_interaction_anova,
  institution_tier_main_effects_anova = institution_tier_main_effects_anova,
  oneway_anova_by_tier = oneway_anova_by_tier,
  kruskal_all_regions_by_tier = kruskal_all_regions_by_tier,
  kruskal_by_region_tier = kruskal_by_region_tier,
  chi_square_nominal_by_region = chi_square_nominal_by_region,
  fisher_nominal_by_region = fisher_nominal_by_region,
  fisher_nominal_by_tier = fisher_nominal_by_tier,
  mann_whitney_by_tier = mann_whitney_by_tier,
  binary_summary = binary_summary,
  binary_tests = binary_tests
)

walk2(
  analysis_tables,
  names(analysis_tables),
  ~ write_csv(.x, file.path("genai_policy_outputs_newcsv", paste0(.y, ".csv")))
)

write_xlsx(
  analysis_tables,
  "genai_policy_outputs_newcsv/genai_policy_newcsv_analysis_tables.xlsx"
)
```
