---
title: "HUDK4051 — Mean GenAI Policy Stance Across Governance Tiers"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 6)
```

# Load Libraries

```{r libraries}
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
```

# Load Data

```{r load}
nyc <- read_excel("GenAI_Policy_Comparative_LearningAnalytics.xlsx",
                  sheet = "NEW_NYC_Coding", skip = 3) %>%
  filter(!is.na(ID)) %>%
  mutate(Region = "NYC")

hk <- read_excel("GenAI_Policy_Comparative_LearningAnalytics.xlsx",
                 sheet = "NEW_HK_Coding", skip = 3) %>%
  filter(!is.na(ID)) %>%
  mutate(Region = "Hong Kong")

df <- bind_rows(nyc, hk) %>%
  filter(Stance %in% c("Prohibitive", "Cautious", "Functional", "Encouraging"))

cat("Total documents:", nrow(df), "\n")
```

# Methodology

Each document's stance was converted to an ordinal numerical score: Prohibitive = 0, Cautious = 1, Functional = 2, Encouraging = 3. This mapping preserves the rank order while permitting aggregation. For each region–tier combination, we computed the mean stance score across all documents assigned to that cell, then plotted the trajectories.

```{r compute}
stance_map <- c("Prohibitive" = 0, "Cautious" = 1,
                "Functional" = 2, "Encouraging" = 3)

tier_order <- c("National/Federal", "City/Territory", "Institutional",
                "Faculty/Department", "Course-wide")

mean_df <- df %>%
  mutate(stance_num = stance_map[Stance],
         Tier = factor(Tier, levels = tier_order)) %>%
  group_by(Region, Tier) %>%
  summarise(mean_stance = mean(stance_num, na.rm = TRUE),
            n = n(), .groups = "drop")

mean_df
```

# Figure: Mean Stance Across Governance Tiers

```{r line-chart}
ggplot(mean_df, aes(x = Tier, y = mean_stance,
                    group = Region, color = Region)) +
  geom_line(linewidth = 1.2) +
  geom_point(aes(shape = Region), size = 4) +
  geom_text(aes(label = sprintf("%.2f", mean_stance)),
            vjust = -1.2, size = 3.5, show.legend = FALSE) +
  scale_color_manual(values = c("Hong Kong" = "#ff7f0e",
                                "NYC" = "#1f77b4")) +
  scale_y_continuous(limits = c(-0.2, 3.3),
                     breaks = seq(0, 3, 0.5)) +
  labs(
    title = "Mean GenAI Policy Stance Across Governance Tiers",
    x = "Governance Tier",
    y = "Mean Stance Score\n(0 = Prohibitive, 3 = Encouraging)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "bottom",
    panel.border = element_rect(
      color = "black",
      fill = NA,
      linewidth = 0.8
    )
  )
```
